---
title: "hw02-Tiantian-Fu"
output: github_document
---

1)Create a data dictionary
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("readr")
library(dplyr)
library(ggplot2)
```
 
2)Import the data in R
```{r}
github <-"https://github.com/ucb-stat133/stat133-fall-2017/raw/master/"
file <- "data/nba2017-player-statistics.csv"
csv <- paste0(github,file)
download.file(url = csv, destfile = 'nba2017-player-statistics.csv')
  
```

```{r}
dat <- read.csv('nba2017-player-statistics.csv',colClasses = c("character","character","factor","character","double",rep('integer',19)))
str(dat)


```

```{r}
dat1 <- read_csv ('nba2017-player-statistics.csv')
dat1$Position <-factor(dat1$Position)
str(dat1)

```
3)Right after importing the data
```{r}
dat$Experience[dat$Experience=='R']<-0
dat$Experience<-factor(dat$Experience)
dat$Experience
```
4)Performance of players
```{r}
Missed_FG = dat$FGA -dat$FGM
Missed_FT = dat$FTA -dat$FTM
PTS = dat$Points2*2+dat$Points3*3+dat$FTM*1
REB = dat$OREB + dat$DREB
MPG = (dat$MIN)/(dat$GP)
EFF =(PTS+REB+(dat$AST)+(dat$STL)+(dat$BLK)-Missed_FG-Missed_FT-(dat$TO))/(dat$GP)
EFF
summary(EFF)
hist(EFF)
```
```{r}
#Display the player name, team, salary,and EFF value of the top-10 players by decreasing order
dat_new <- mutate(dat,EFF)
dat_new1 <- arrange(dat_new,desc(EFF))
display_A <- select(slice(dat_new1,1:10),Player,Team,Salary,EFF)
display_A

#Provide the names of the players that have a negative EFF.
select(filter(dat_new,EFF<0),Player)

#Use the function cor() to compute the coreelation coefficients betweeen EFF and all the variables used in teh EFF formula.
cor_table <-data.frame(
  PTS=cor(EFF,PTS),
  REB=cor(EFF,REB),
  AST=cor(EFF,dat$AST),
  STL=cor(EFF,dat$STL),
  BLK=cor(EFF,dat$BLK),
  Missed_FG=cor(EFF,-Missed_FG),
  Missed_FT=cor(EFF,-Missed_FT),
  TO=cor(EFF,-dat$TO)
)
cor_table
?sort
cor_table[1,]  = sort(cor_table[1,], decreasing = TRUE)



#Barplot it
barplot(as.numeric(cor_table),
        ylim=c(-1,1),
        main= "Correlations betwwen Players Stats and EFF",
        names.arg = variable.names(cor_table),
        col=ifelse(as.numeric(cor_table)>0,"grey","coral1"),
        border=NA,
        cex.names = 0.5)
```

5)Efficiency and Salary
```{r}
#scatterplot between efficiency and salary
ggplot(data = dat_new, aes(x=EFF,y=Salary) )+
  geom_point()+
  geom_smooth(method = loess)
cor(dat_new$EFF,dat_new$Salary)
#they have kind of strong positive relationship

#MPG players
dat_new <- mutate(dat_new,MPG)
Players2 <-(filter(dat_new,MPG >= 20))
Players2
ggplot(data = Players2, aes(x=EFF,y=Salary) )+
  geom_point()+
  geom_smooth(method = loess)
cor(Players2$EFF,Players2$Salary)
#it has less strong positive relationship between more established players.
```
6)Comments and Reflections
1.I think finding the correlations between EFF and other different variables is the hardest.

2.reading tables by using basis

3.yes, I got help from GSI

4.I spent 5 hours doing this HW

5.reading data and find the correlations

6.still confused about reading data

7.the fourth question

8.The last part.


