---
title: "Warmup2"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# assembling url (so it fits on the screen)
github <- 'https://github.com/ucb-stat133/stat133-hws-fall17/'
repo <- 'raw/master/warmup02/data/nba2017-salary-points.RData'
download.file(
  url = paste0(github, repo),
  destfile = "nba2017-salary-points.RData")

# load the objects
load("nba2017-salary-points.RData")

# list the available objects
ls()
```
#Quantitative Variable
```{r}
summary(points)
sd(points,na.rm = FALSE)
hist(points)
boxplot(points)
```
#Qualitative Variable
```{r}
factor(position)
table(position)
table(position)/441
barplot(table(position))

```

* I think that the process to analyse data and make a report is the hardest thing, even though we are pretty much sure how we should write a proper report.
* I think that find some certain functions by using help is the easy part even though, we did not cover a lot during the class.
* The error I was struggling with is how to find and use the density function.
* I do not really understand how to describe data 
* The most time consuming part is write a summary
* I did not collaborate with other students
* It was all right.

